Twisted 11-dimensional supergravity, I

### 2021-08-05 draft.tex
bf theory

Consider the following cochain complex $\cE_{pot}$:
\beqn\label{eqn:E}
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
\end{tikzcd}
\eeqn
We will write the fields using the notation
\begin{align*}
(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
\end{align*}

Let 
\[
\begin{array}{rccc}
\int^\Omega \colon \Omega^{0,\bu}(X) & \to & \CC [6] \\
\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
\end{array}
\]
be integration along the holomorphic volume form.

Define the pairing 
\[
\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
\]
by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$

@@

Define the map of cochain complexes
\[
\Phi \colon \cE_{pot} \to \til{\cE}_{KS}
\]
by the formulas
\[
\Phi (\mu,\nu) = \mu + u \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
\]
In the last expression we have used the isomorphism
\[
(-) \vee \Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu} 
\]
so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.

@@

A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is linear combination of functionals of the form
\[
\int_\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
\]
Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
\begin{align*}
\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
\end{align*}
The first constraint ensures that the integrand is of top polyvector degree. 
The second constraint is on the descendant degree, see \brian{ref above}.

@@

@@

>>>>

Consider the following cochain complex $\cE_{pot}$:
\beqn\label{eqn:E}
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
\end{tikzcd}
\eeqn
We will refer to the components of the fields using the notation
\begin{align*}
(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
\end{align*}
The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree.

Let 
\[
\begin{array}{rccc}
\int^\Omega \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
\end{array}
\]
be integration along the holomorphic volume form. 
Define the pairing 
\[
\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
\]
by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$

@@

Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
by the formulas
\[
\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
\]
In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.

@@

A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
\[
\int_\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
\]
Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
\begin{align*}
\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
\end{align*}
The first constraint ensures that the integrand is of top polyvector degree. 
The second constraint is on the descendant degree, see \brian{ref above}.

@@

\subsubsection{}
\label{sec:Linfty}

@@

\subsubsection{}
Suppose that $\fg$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\fg_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
The graded vector space $\fg \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
\begin{align*}
[x \otimes a]_1 & = [x]^\fg_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\fg_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
\end{align*}

We apply this construction to the case of the $L_\infty$ algebra $\cL_0 = \cL_0 (X)$ of \S \ref{sec:Linfty} resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ and the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold. 
We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.

Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
We recall the construction. 
Let $\cL$ be any local $L_\infty$ algebra, it is the sheaf of sections of some graded vector bundle $L$. 
For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
\[
\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
\]

The fields of the associated BV theory are pairs
\[
  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
\]
Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.

The action functional reads $S_{\rm BF} = \int B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
